\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-08 forwards-and-backwards.tex
Update on Overleaf.

%%%%%%% notation
\newcommand{\DG}{\mathcal{B}}  % generator of the dispersal process
\newcommand{\meanq}{\vec b}    % mean of dispersal, times theta
\newcommand{\covq}{\Sigma}     % covariance matrix of dispersal, times theta
\newcommand{\kernel}{\varrho}  % interaction kernels
\newcommand{\smooth}[1]{\kernel_{#1} \! * \!}  % convolution by the interaction kernel
\newcommand{\wavespeed}{\mathfrak{c}}    % speed (vector) of a wave
\newcommand{\Lgen}{\mathcal{L}}    % generator of a lineage
\newcommand{\Pgen}{\mathcal{P}}    % generator of the population process

@@

\begin{definition}[Martingale Problem Characterisation]
    \label{Def: Rescaled Models}
We define $(\eta^{\theta}_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
with initial condition $\eta^{\theta}_0$,
such that for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$,
\begin{equation}
    \label{eq: Pre-limit Martingale Characterisation}
\begin{aligned}
M^{\theta}_t(f)
&:=  \langle f,\eta^{\theta}_t \rangle
        -\langle f,\eta^{\theta}_0 \rangle
 \\ &\qquad {}
 -  \int_{0}^{t}\bigg\{
        \int\left(   \int \theta
     \left(
        f(z)r\big(z,\varrho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\varrho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
        \\ & \qquad \qquad \qquad \qquad {} \times
                            \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)
     \\ & \qquad {} +\int 
     f(x)F\big(x,\varrho_{F}*\eta^{\theta}_{s}(x)\big)
     \eta^{\theta}_{s}(dx)
    \bigg\} ds
\end{aligned}    
\end{equation}
is a martingale with quadratic variation
\begin{equation}
\begin{aligned} \relax
[ M^{\theta}_t(f)] =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
\langle \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\varrho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds. 
\end{aligned}    
\end{equation}

@@

\begin{theorem} \label{thm:nonlocal_convergence}
    Let $(\eta^\theta_t)_{t \geq 0}$
    be as defined in Definition \ref{def:model_setup}
    and assume that as $\theta \to \infty$, $N \to \infty$
    in such a way that $\theta/N \to \delta$.
    (However, interaction distances $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$
    remain constant.)

    The sequence of stochastic processes
    $(\eta^\theta_t)_{t \geq 0}$
    converges along subsequences in distribution as $\theta \to \infty$
    to a measure-valued process $(\eta_t)_{t \geq 0}$
    which satisfies that, for every $f:\mathbb{R}^d \rightarrow \mathbb{R}$,
    \begin{align} \label{eqn:mgale_problem}
        M_t
        &:=
        \langle f(x), \eta_t(dx) \rangle
        -
        \langle f(x), \eta_0(dx) \rangle
        \\ & \qquad
        -
        \int_0^t \big\langle
            \gamma(x, \smooth{\gamma} \eta_{s}(x))
            \mathcal{B}\left(
                f(\cdot) r(\cdot, \smooth{r} \eta_{s}(\cdot))
            \right)(x)
            +
            f(x)
            F(x, \smooth{F} \eta_{s}(x)),
            \eta_{s}(dx)
        \big\rangle ds,
    \end{align}
    is a martingale.
    The quadratic variation of $M_t$ is given by 
    \begin{align} \label{eqn:mgale_variation}
        [ M ]_t
        =
        \delta
        \int_0^t
        \big\langle
            \gamma\left( x, \smooth{\gamma} \eta_{s}(x) \right)
            r\left(x, \smooth{r} \eta_{s}(x) \right)
            f^2(x),
            \eta_{s} (dx)
        \big\rangle ds. 
    \end{align}
    In other words, the limit is a measure-valued process with non-local interactions.
    Furthermore, if $\delta = 0$ the limit is deterministic.
\end{theorem}

@@

\comment{
    \textbf{Question:}
    In our outline
    we said this corollary would be about uniqueness,
    but is it also about continuity of the limit (i.e., existence of a density)?
    A lot of my uncertainty in how to phrase these results
    comes from being unsure what exactly we can say about densities.
}

\begin{corollary}[Deterministic limits]
    \label{cor:nonlocal_pde_limits}
    In the context of Theorem~\ref{thm:nonlocal_convergence},
    if the limit is deterministic (i.e., $\theta / N \to \delta = 0$), $\eta_0$ has a density,
    and \comment{additional conditions? can we say something like this??}
    then any limit $\eta_t(dx)$ has a density $\varphi(t, x)$,
    which is a weak solution to the nonlocal partial differential equation
    \begin{equation} \label{eqn:nonlocal_pde}
        \partial_t \varphi(t, x)
        =
        r\left(x, \smooth{r} \varphi(t,x) \right)
        \mathcal{B} \left[
            \varphi(t, \cdot)
            \gamma\big( x, \smooth{\gamma} \varphi(t, \cdot) \big)
        \right](x)
        +
        \varphi(t, x)
        F\left(x, \smooth{F} \varphi(t,x) \right)
        .
    \end{equation}
    If equation \eqref{eqn:nonlocal_pde} has a unique solution,
    then $(\eta^\theta_t)_{t \ge 0}$ converges to that solution.

@@

@@

A lineage is, in general, a well-defined stochastic process,
but there are two important questions
that affect its tractability.
First, when is it a Markov process given the population process?
(I.e., given $(\eta_t)_{t=0^T}$ that records numbers of individuals
but not their ancestry.)
We expect the answer here to be that a lineage is Markov
only in the $N \to \infty$ limit.
\comment{(or, do we know this? we can cite Barton, Depaulis and Etheridge at least for discussion.)}
Second, does the process have a tractable description?
If the population process has a density,
then it turns out that a lineage is a diffusion driven by the density.
The remaining case is the superprocess limit ($\theta/N \to \delta > 0$);
in this case, we expect that a lineage could still be described as a generalized diffusion,
but moving within a stochastic landscape that is singular in $d \ge 2$.
We focus on the more tractable situation where the population process is deterministic.
However, the results here apply to either the local or nonlocal case
(i.e., where the density solves a local or nonlocal PDE).

@@

A Taylor expansion allows us to write
\begin{multline*}
    \Pgen^\theta
    F(\langle f,\eta \rangle)
    =
    F'(\langle f, \eta \rangle)
    \lim_{\delta t\downarrow 0} \frac{1}{\delta t}
    \IE\left[
        \left. \langle f, \eta_{\delta t} \rangle
        -
        \langle f, \eta \rangle
        \right| \eta_0=\eta
    \right]
    \\
    \qquad {}
    + \frac{1}{2}
        F''(\langle f,\eta\rangle)
    \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
    \IE\left[
        \left.\big(\langle f,\eta_{\delta t}\rangle
        -
        \langle f, \eta\rangle\big)^2 \right|\eta_0=\eta
    \right]
    +
    \varepsilon_{\theta}(f, F, \eta),
\end{multline*}
where the terms that make up 
$\varepsilon_{\theta, N}(f, F, \eta)$
will be negligible in our scaling limit.

@@

We use the fact that $\int q_\theta(x,dz)=1$ to rewrite~(\ref{mean measure})
as 
\begin{equation}
\label{eqn:rewritten mean measure}
\begin{split}
    \int\left(
        \int \theta \left( f(z) r(z,\eta)- f(x) r(x,\eta) \right) q_\theta(x,dz)
    \right)
    \gamma(x,\eta)
    \eta(dx)
    \\
    + \int \int f(x) \theta \Big(
        r(x,\eta) \gamma(x,\eta)
        - \mu_\theta(x,\eta)
    \Big) \eta(dx).
\end{split}
\end{equation}
We have defined $\mu_\theta$ so that the second term is simple:
\begin{align*}
    \theta \Big( r(x,\eta) \gamma(x,\eta) - \mu_\theta(x,\eta) \Big)
    = F(x, \eta) .
\end{align*}
This definition --
is really a `near-critical' assumption that birth and death rates
differ by something of order $1/\theta$.
Furthermore, since we've taken $q_\theta$ to be the density of a Normal
with mean and variance proportional to $1/\theta$,
\begin{align} \label{eqn:near_critical}
    \int \theta \Big(
        r(z,\eta) f(z)
        -
        r(x,\eta) f(x)
    \Big) q_\theta(x,dz) 
    \qquad \stackrel{\theta\to\infty}{\longrightarrow} \qquad  
    \DG \big(r(\cdot,\Xi)f(\cdot)\big)(x),
\end{align}
where recall if dispersal is simply standard multivariate Gaussian
with mean zero and covariance $\sigma^2 I / \theta$,
then $\DG = \sigma^2 \Delta$, where $\Delta$ denotes the Laplacian.
Note that there is a slight mismatch between the locations at which we are 
measuring birth and death rates, because in~\eqref{eqn:near_critical}
the establishment probability is 
measured at $x$ rather than at the point where juveniles fall. 
\comment{(IS THIS BIT STILL TRUE:)}
This condition also differs from the assumption that
we use in~\S\ref{scalings with levels} to guarantee convergence of the 
processes with levels in our lookdown 
constructions, see~(\ref{lookdown blambda}). 
Under mild
regularity conditions on $r$ (which we certainly need to have sensible 
limiting models) the conditions are equivalent.

@@

We now look at the second order term.
An individual at location $x$ gives birth 
to a surviving offspring at $y$ at rate
$$
\gamma(x,\eta) r(y,\eta) q_{\theta}(x, dy) ,
$$
and since this increments $\langle f, \eta \rangle$ by $f(y) / N$,
the contribution to the quadratic variation from birth events,
which occur at rate $\theta$ per individual 
(so, rate $N\theta |\eta|$ overall), is
$$
\langle
    N \theta \gamma(x,\eta)
    \int \frac{1}{N^2} f^2(y) r(y,\eta)
    q_\theta(x,dy) 
    , \eta(dx)
\rangle .
$$
Similarly, the increment in $\langle f, \eta\rangle$ resulting from 
the death of an individual at $x$ is $f(x)/N$, and so combining with the 
above, the second order term in the generator takes the form
$$
F''(\langle f,\eta\rangle)
\frac{1}{2} N \theta
\left\{
    \langle
        \gamma(x,\eta)
        \int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
    , \eta(dx)\rangle
    +
    \langle
        \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
    ,\eta(dx)\rangle
\right\} .
$$
The term $\varepsilon_{\theta,N}(f, F, \eta)$ will be 
$\bigO(\theta/N^2)$.

@@

If $N=\delta\theta$, for some positive constant $\delta$,
the second order term in the generator remains order
one as $\theta\to\infty$, and  
we expect a `generalised superprocess' limit.
Assuming some regularity of the coefficients (in particular of $r$), 
the second order term in the generator will take the form
$$
\frac{1}{\delta}F''(\langle f,\Xi\rangle)
\langle f^2(x), \gamma(x,\Xi)
r(x,\Xi)\Xi(dx)\rangle.
$$
That is
$$\langle f(x), \Xi_t(dx)\rangle-\langle f(x), \Xi_0(dx)\rangle
-\int_0^t\langle\gamma(x,\Xi_s)\DG\big(r(\cdot,\Xi_s)f(\cdot)\big)(x),
\Xi_s(dx)\rangle ds$$
is a martingale with quadratic variation
$$\frac{2}{\delta}\int_0^t\langle f^2(x) 
\gamma(x,\Xi_s)r(x,\Xi_s),\Xi_s(dx)\rangle ds.$$

@@

To scale our lookdown model to be consistent with
the spatial model described in \S \ref{sec: Model and main results},
we will let $\lambda$ takes on the role of $N$
in \S \ref{sec: Model and main results},
i.e. each individual has mass $1/\lambda$
in the scaling limit.
Time is once again scaled by $\theta$,
and the birth, death and establishment rates 
depend on local densities given by
mollification over Gaussian kernels with radius
$\varepsilon_{\gamma}$, $\varepsilon_{F}$ and $\varepsilon_{r}$.

Explicitly, in the $\theta$-th stage of re-scaling,
an individual has mass $\frac{1}{\lambda} := \frac{1}{N}$
and a level between $[0,N]$;
the established birth rate $\gamma(x,\eta)$ is
$$\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)
:=~\theta\gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy);$$
the local branching mechanism $b(x,\eta)$ is 
$$b_{\theta}(x, \eta):=~ \theta \bigg\{ \gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy)-\mu(x, \eta)\bigg\};$$
and the dispersal kernel $q^{\mathfrak{m}}(x,\eta, dy)$ is 
$$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) 
:=~ \frac{r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$

@@

The main interest in using a lookdown construction for our 
population processes is that it allows us to retain information 
about relatedness between individuals as we pass to the infinite
density limit. In order to exploit this, we generalise the construction of 
stochastic equations presented in \S \ref{sec: Evolution of an Individual Particle} to the infinite density limit.\\
In the scaling limit $A^{\text{nl}}_{\varepsilon}$, the spatial movement of particles can be characterised with the map $$h \mapsto \gamma\big(x,(\varrho_{\varepsilon}*\Xi)(x)\big)r\big(x,(\varrho_{\varepsilon}*\Xi)(x)\big)\mathcal{B}^{m}_{\varepsilon}(\Xi)h(x) ,$$
and as individual particles travel as a random walk in the pre-limit model, we should expect a diffusion limit for individual trajectories.
\todo[inline]{From Terence: we should try explain in detail why this is the generator of an individual line of descent forward-in-time. The main question here is whether we should have a factor of $r$ in the above notation. For the proof to work in \S \ref{sec: motion of ancestral lineages} we will need a factor of $r$ but I have been finding it slightly unintuitive particularly since the effect of $r$ has been accounted into $\mathcal{B}^{\mathfrak{m}}$ through the limit.}
To simply notation, we let the above map be the generator of a process 
satisfying 
\[X(t)=X(0)+\int_0^t\sigma (X(s),\Xi (s))dW(s)+\int\beta (X(s),\Xi 
(s))ds.\]
\begin{remark}
In particular recall that as in Remark \ref{Remark: Product Rule on Laplacian}, if $\mathcal{B}$ is the Laplacian operator, then the generator above is merely 
$$\gamma\big(x,(\varrho_{\varepsilon}*\Xi)(x)\big)\left(\Delta h(x) +2 \nabla h(x) \cdot \nabla \log r( \cdot, (\varrho_{\varepsilon}*\Xi)(\cdot))(x)\right),$$
and applying Ito's formula we have 
\begin{equation}\label{eq: Individual lineage generator description}
\begin{aligned}
\beta(X(s),\Xi(s))=& 2\gamma\big(X(s),(\varrho_{\varepsilon}*\Xi)(X(s))\big) \nabla \log r (\cdot, (\varrho_{\varepsilon}*\Xi)(\cdot))(X(s))\\
\sigma(X(s),\Xi(s))=& \sqrt{2\gamma\big(X(s),(\varrho_{\varepsilon}*\Xi)(X(s))\big)}.
\end{aligned}
\end{equation}
\end{remark}
Furthermore, recall that in our scaling limit, 
\begin{equation}
\begin{aligned}
\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s), \eta(s)) &\to \ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)),\\
b_{\theta}(X_{\tau}(s),\eta(s)) &\to  F(X_{\tau}(s), (\varrho_{\varepsilon}*\eta)(X_{\tau}(s)))\\
&+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\eta)(\cdot))(X_{\tau}(s)).
\end{aligned}    
\end{equation}

@@

\subsubsection{Compact Containment Condition}
Before proving compact containment condition,
we first prove a technical lemma that involves a bound on the Gaussian kernels.
\begin{lemma}
    \label{lem: gamma - r radius comparison}
    Assume that $\varepsilon_{r}^2 + \frac{1}{\theta} < \varepsilon_{\gamma}^2,$ then
    for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d)$
    and for all $\eta \in \mathcal{M}_{f}(\mathbb{R}^d)$, we have

>>>>

%%%%%%% notation
\newcommand{\DG}{\mathcal{B}}  % generator of the dispersal process
\newcommand{\meanq}{\vec b}    % mean of dispersal, times theta
\newcommand{\covq}{\Sigma}     % covariance matrix of dispersal, times theta
\newcommand{\kernel}{\rho}  % interaction kernels
\newcommand{\smooth}[1]{\kernel_{#1} \! * \!}  % convolution by the interaction kernel
\newcommand{\wavespeed}{\mathfrak{c}}    % speed (vector) of a wave
\newcommand{\Lgen}{\mathcal{L}}    % generator of a lineage
\newcommand{\Pgen}{\mathcal{P}}    % generator of the population process

@@

\begin{definition}[Martingale Problem Characterisation]
    \label{Def: Rescaled Models}
We define $(\eta^{\theta}_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
with initial condition $\eta^{\theta}_0$,
such that for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$,
\begin{equation}
    \label{eq: Pre-limit Martingale Characterisation}
\begin{aligned}
M^{\theta}_t(f)
&:=  \langle f,\eta^{\theta}_t \rangle
        -\langle f,\eta^{\theta}_0 \rangle
 \\ &\qquad {}
 -  \int_{0}^{t}\bigg\{
        \int\left(   \int \theta
     \left(
        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
        \\ & \qquad \qquad \qquad \qquad {} \times
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)
     \\ & \qquad {} +\int 
     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
     \eta^{\theta}_{s}(dx)
    \bigg\} ds
\end{aligned}    
\end{equation}
is a martingale with quadratic variation
\begin{equation}
\begin{aligned} \relax
[ M^{\theta}_t(f)] =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds. 
\end{aligned}    
\end{equation}

@@

\begin{theorem} \label{thm:nonlocal_convergence}
    Let $(\eta^\theta_t)_{t \geq 0}$
    be as defined in Definition \ref{def:model_setup}
    and assume that as $\theta \to \infty$, $N \to \infty$
    in such a way that $\theta/N \to \alpha$.
    (However, interaction distances $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$
    remain constant.)

    The sequence of stochastic processes
    $(\eta^\theta_t)_{t \geq 0}$
    converges along subsequences in distribution as $\theta \to \infty$
    to a measure-valued process $(\eta_t)_{t \geq 0}$
    which satisfies that, for every $f:\mathbb{R}^d \rightarrow \mathbb{R}$,
    \begin{align} \label{eqn:mgale_problem}
        M_t
        &:=
        \langle f(x), \eta_t(dx) \rangle
        -
        \langle f(x), \eta_0(dx) \rangle
        \\ & \qquad
        -
        \int_0^t \big\langle
            \gamma(x, \smooth{\gamma} \eta_{s}(x))
            \mathcal{B}\left(
                f(\cdot) r(\cdot, \smooth{r} \eta_{s}(\cdot))
            \right)(x)
            +
            f(x)
            F(x, \smooth{F} \eta_{s}(x)),
            \eta_{s}(dx)
        \big\rangle ds,
    \end{align}
    is a martingale.
    The quadratic variation of $M_t$, denoted $\langle M \rangle_t$, is given by 
    \begin{align} \label{eqn:mgale_variation}
        \langle M \rangle_t
        =
        \alpha
        \int_0^t
        \big\langle
            \gamma\left( x, \smooth{\gamma} \eta_{s}(x) \right)
            r\left(x, \smooth{r} \eta_{s}(x) \right)
            f^2(x),
            \eta_{s} (dx)
        \big\rangle ds. 
    \end{align}
    In other words, the limit is a measure-valued process with non-local interactions.
    Furthermore, if $\alpha = 0$ the limit is deterministic.
\end{theorem}

@@

\comment{
TODO: insert definition of "weak solution of the PDE \ref{eqn:nonlocal_pde}" heere.
}

\begin{corollary}[Deterministic limits]
    \label{cor:nonlocal_pde_limits}
    \comment{(TODO: remove "has a density" and rephrase appropriately)}
    In the context of Theorem~\ref{thm:nonlocal_convergence},
    if the limit is deterministic (i.e., $\theta / N \to \alpha = 0$), $\eta_0$ has a density,
    and \comment{additional conditions? can we say something like this??}
    then any limit $\eta_t(dx)$ has a density $\varphi(t, x)$,
    which is a weak solution to the nonlocal partial differential equation
    \begin{equation} \label{eqn:nonlocal_pde}
        \partial_t \varphi(t, x)
        =
        r\left(x, \smooth{r} \varphi(t,x) \right)
        \mathcal{B} \left[
            \varphi(t, \cdot)
            \gamma\big( x, \smooth{\gamma} \varphi(t, \cdot) \big)
        \right](x)
        +
        \varphi(t, x)
        F\left(x, \smooth{F} \varphi(t,x) \right)
        .
    \end{equation}
    If equation \eqref{eqn:nonlocal_pde} has a unique solution,
    then $(\eta^\theta_t)_{t \ge 0}$ converges to that solution.

@@

\comment{TODO: Tom has conditions (coefficient are Lipschitz?) under which
    the solution to \eqref{eqn:nonlocal_pdf} has a density (Thm 2.1 in DDMOT);
    should we insert those here (as a Corollary or Proposition, maybe?)}

@@

A lineage is, in general, a well-defined stochastic process,
but there are two important questions
that affect its tractability.
First, when is it a Markov process given the population process?
(I.e., given $(\eta_t)_{t=0^T}$ that records numbers of individuals
but not their ancestry.)
We expect the answer here to be that a lineage is Markov
only in the $N \to \infty$ limit.
\comment{(or, do we know this? we can cite Barton, Depaulis and Etheridge at least for discussion.)}
Second, does the process have a tractable description?
If the population process has a density,
then it turns out that a lineage is a diffusion driven by the density.
The remaining case is the superprocess limit ($\theta/N \to \alpha > 0$);
in this case, we expect that a lineage could still be described as a generalized diffusion,
but moving within a stochastic landscape that is singular in $d \ge 2$.
We focus on the more tractable situation where the population process is deterministic.
However, the results here apply to either the local or nonlocal case
(i.e., where the density solves a local or nonlocal PDE).

@@

A Taylor expansion allows us to write
\begin{multline*}
    \Pgen^\theta
    F(\langle f,\eta \rangle)
    =
    F'(\langle f, \eta \rangle)
    \lim_{\delta t\downarrow 0} \frac{1}{\delta t}
    \IE\left[
        \left. \langle f, \eta_{\delta t} \rangle
        -
        \langle f, \eta \rangle
        \right| \eta_0=\eta
    \right]
    \\
    \qquad {}
    + \frac{1}{2}
        F''(\langle f,\eta\rangle)
    \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
    \IE\left[
        \left.\big(\langle f,\eta_{\delta t}\rangle
        -
        \langle f, \eta\rangle\big)^2 \right|\eta_0=\eta
    \right]
    +
    \epsilon_{\theta}(f, F, \eta),
\end{multline*}
where the terms that make up 
$\epsilon_{\theta, N}(f, F, \eta)$
will be negligible in our scaling limit.

@@

We use the fact that $\int q_\theta(x,dz)=1$ to rewrite~(\ref{mean measure})
as 
\begin{equation}
\label{eqn:rewritten mean measure}
\begin{split}
    \int\left(
        \int \theta \left( f(z) r(z,\eta)- f(x) r(x,\eta) \right) q_\theta(x,dz)
    \right)
    \gamma(x,\eta)
    \eta(dx)
    \\
    + \int \int f(x) \theta \Big(
        r(x,\eta) \gamma(x,\eta)
        - \mu_\theta(x,\eta)
    \Big) \eta(dx).
\end{split}
\end{equation}
We have defined $\mu_\theta$ so that the second term is simple:
\begin{align*}
    \theta \Big( r(x,\eta) \gamma(x,\eta) - \mu_\theta(x,\eta) \Big)
    = F(x, \eta) .
\end{align*}
This definition --
is really a `near-critical' assumption that birth and death rates
differ by something of order $1/\theta$.
Furthermore, since we've taken $q_\theta$ to be the density of a Normal
with mean and variance proportional to $1/\theta$,
\begin{align} \label{eqn:near_critical}
    \int \theta \Big(
        r(z,\eta) f(z)
        -
        r(x,\eta) f(x)
    \Big) q_\theta(x,dz) 
    \qquad \stackrel{\theta\to\infty}{\longrightarrow} \qquad  
    \DG \big(r(\cdot,\Xi)f(\cdot)\big)(x),
\end{align}
where recall if dispersal is simply standard multivariate Gaussian
with mean zero and covariance $\sigma^2 I / \theta$,
then $\DG = \sigma^2 \Delta$, where $\Delta$ denotes the Laplacian.
Note that there is a slight mismatch between the locations at which we are 
measuring birth and death rates, because in~\eqref{eqn:near_critical}
the establishment probability is 
measured at $x$ rather than at the point where juveniles fall.

@@

We now look at the second order term.
An individual at location $x$ gives birth 
to a surviving offspring at $y$ at rate
$$
\gamma(x,\eta) r(y,\eta) q_{\theta}(x, dy) ,
$$
and since this increments $\langle f, \eta \rangle$ by $f(y) / N$,
the contribution to the quadratic variation from birth events,
which occur at rate $\theta$ per individual 
(so, rate $N\theta |\eta|$ overall), is
$$
\langle
    N \theta \gamma(x,\eta)
    \int \frac{1}{N^2} f^2(y) r(y,\eta)
    q_\theta(x,dy) 
    , \eta(dx)
\rangle .
$$
Similarly, the increment in $\langle f, \eta\rangle$ resulting from 
the death of an individual at $x$ is $f(x)/N$, and so combining with the 
above, the second order term in the generator takes the form
$$
F''(\langle f,\eta\rangle)
\frac{1}{2} N \theta
\left\{
    \langle
        \gamma(x,\eta)
        \int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
    , \eta(dx)\rangle
    +
    \langle
        \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
    ,\eta(dx)\rangle
\right\} .
$$
The term $\epsilon_{\theta,N}(f, F, \eta)$ will be 
$\bigO(\theta/N^2)$.

@@

If $N=\alpha\theta$, for some positive constant $\alpha$,
the second order term in the generator remains order
one as $\theta\to\infty$, and  
we expect a `generalised superprocess' limit.
Assuming some regularity of the coefficients (in particular of $r$), 
the second order term in the generator will take the form
$$
\frac{1}{\alpha}F''(\langle f,\Xi\rangle)
\langle f^2(x), \gamma(x,\Xi)
r(x,\Xi)\Xi(dx)\rangle.
$$
That is
$$\langle f(x), \Xi_t(dx)\rangle-\langle f(x), \Xi_0(dx)\rangle
-\int_0^t\langle\gamma(x,\Xi_s)\DG\big(r(\cdot,\Xi_s)f(\cdot)\big)(x),
\Xi_s(dx)\rangle ds$$
is a martingale with quadratic variation
$$\frac{2}{\alpha}\int_0^t\langle f^2(x) 
\gamma(x,\Xi_s)r(x,\Xi_s),\Xi_s(dx)\rangle ds.$$

@@

To scale our lookdown model to be consistent with
the spatial model described in \S \ref{sec: Model and main results},
we will let $\lambda$ takes on the role of $N$
in \S \ref{sec: Model and main results},
i.e. each individual has mass $1/\lambda$
in the scaling limit.
Time is once again scaled by $\theta$,
and the birth, death and establishment rates 
depend on local densities given by
mollification over Gaussian kernels with radius
$\epsilon_{\gamma}$, $\epsilon_{F}$ and $\epsilon_{r}$.

Explicitly, in the $\theta$-th stage of re-scaling,
an individual has mass $\frac{1}{\lambda} := \frac{1}{N}$
and a level between $[0,N]$;
the established birth rate $\gamma(x,\eta)$ is
$$\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)
:=~\theta\gamma(x, \rho_{\gamma}*\eta(x)) \int r(y, \rho_{r}*\eta(y))q_{\theta}(x,dy);$$
the local branching mechanism $b(x,\eta)$ is 
$$b_{\theta}(x, \eta):=~ \theta \bigg\{ \gamma(x, \rho_{\gamma}*\eta(x)) \int r(y, \rho_{r}*\eta(y))q_{\theta}(x,dy)-\mu(x, \eta)\bigg\};$$
and the dispersal kernel $q^{\mathfrak{m}}(x,\eta, dy)$ is 
$$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) 
:=~ \frac{r(y,\rho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\rho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$

@@

The main interest in using a lookdown construction for our 
population processes is that it allows us to retain information 
about relatedness between individuals as we pass to the infinite
density limit. In order to exploit this, we generalise the construction of 
stochastic equations presented in \S \ref{sec: Evolution of an Individual Particle} to the infinite density limit.\\
In the scaling limit $A^{\text{nl}}_{\epsilon}$, the spatial movement of particles can be characterised with the map $$h \mapsto \gamma\big(x,(\rho_{\epsilon}*\Xi)(x)\big)r\big(x,(\rho_{\epsilon}*\Xi)(x)\big)\mathcal{B}^{m}_{\epsilon}(\Xi)h(x) ,$$
and as individual particles travel as a random walk in the pre-limit model, we should expect a diffusion limit for individual trajectories.
\todo[inline]{From Terence: we should try explain in detail why this is the generator of an individual line of descent forward-in-time. The main question here is whether we should have a factor of $r$ in the above notation. For the proof to work in \S \ref{sec: motion of ancestral lineages} we will need a factor of $r$ but I have been finding it slightly unintuitive particularly since the effect of $r$ has been accounted into $\mathcal{B}^{\mathfrak{m}}$ through the limit.}
To simply notation, we let the above map be the generator of a process 
satisfying 
\[X(t)=X(0)+\int_0^t\sigma (X(s),\Xi (s))dW(s)+\int\beta (X(s),\Xi 
(s))ds.\]
\begin{remark}
In particular recall that as in Remark \ref{Remark: Product Rule on Laplacian}, if $\mathcal{B}$ is the Laplacian operator, then the generator above is merely 
$$\gamma\big(x,(\rho_{\epsilon}*\Xi)(x)\big)\left(\Delta h(x) +2 \nabla h(x) \cdot \nabla \log r( \cdot, (\rho_{\epsilon}*\Xi)(\cdot))(x)\right),$$
and applying Ito's formula we have 
\begin{equation}\label{eq: Individual lineage generator description}
\begin{aligned}
\beta(X(s),\Xi(s))=& 2\gamma\big(X(s),(\rho_{\epsilon}*\Xi)(X(s))\big) \nabla \log r (\cdot, (\rho_{\epsilon}*\Xi)(\cdot))(X(s))\\
\sigma(X(s),\Xi(s))=& \sqrt{2\gamma\big(X(s),(\rho_{\epsilon}*\Xi)(X(s))\big)}.
\end{aligned}
\end{equation}
\end{remark}
Furthermore, recall that in our scaling limit, 
\begin{equation}
\begin{aligned}
\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s), \eta(s)) &\to \ell \gamma(X_{\tau}(s),\rho_\epsilon*\Xi(X_{\tau}(s)),\\
b_{\theta}(X_{\tau}(s),\eta(s)) &\to  F(X_{\tau}(s), (\rho_{\epsilon}*\eta)(X_{\tau}(s)))\\
&+\gamma(X_{\tau}(s), (\rho_{\epsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\rho_{\epsilon}*\eta)(\cdot))(X_{\tau}(s)).
\end{aligned}    
\end{equation}

@@

\subsubsection{Compact Containment Condition}
Before proving compact containment condition,
we first prove a technical lemma that involves a bound on the Gaussian kernels.
\begin{lemma}
    \label{lem: gamma - r radius comparison}
    Assume that $\epsilon_{r}^2 + \frac{1}{\theta} < \epsilon_{\gamma}^2,$ then
    for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d \times \mathbb{R})$
    with bounded first and second derivatives
    and for all $\eta \in \mathcal{M}_{f}(\mathbb{R}^d)$, we have
